Untitled

### 2021-02-26 outputs/paper/paper.Rmd
Commit for data findings

A presurvey with five questions was conducted before the decision on intervention was made. The purpose was to make sure our assumptions about the resturant similarities between Petereborough and Brantford are based on concert evidence. We asked selected respondents about the restaurants' location, employment, sales, service types, average price per meal per person to assess whether the resturuants in the two cities are of considerable similarities.

@@

@@

* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar qualities. However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis. In other words, we believe the response rate within the different restaurant subgroups to be the same. Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of the results.

* The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations. Restaurants that lost their businesses during the pandemic could not be captured with the current method. However, these may be the ones that are most severely impacted. Another aspect of the survivorship bias involves the use of the same sampling frame for the presurvey and the formal survey. Since there is a three-month time lag, some resturuants may be closed during that time.

@@

>>>>

A presurvey with five questions was conducted before the decision on intervention was made. The purpose was to make sure our assumptions about the resturant similarities between Peterborough and Brantford are based on concert evidence. We asked selected respondents about the restaurants' location, employment, sales, service types, average price per meal per person to assess whether the resturuants in the two cities are of considerable similarities.

@@

```{r}
simulated_dataset %>%
  tabyl(q1_city, q11_rate_support)%>%
  adorn_totals("row")%>%
  adorn_totals("col")%>%
  adorn_percentages("row")%>%
  adorn_pct_formatting(digits=2)%>%
  adorn_ns()%>%
  adorn_title("combined",row_name = "City", col_name = "Rating")%>%
  kable("html", align = 'ccccccc', caption = 'Number or percentage of each rating level')%>%
  kable_styling(full_width = F)
```

 As an agent to gather relevant feedback to the Ontario Government, we asked restaurants how they found the governmental support programs so far. According to Table, both cities stated the effectiveness of the governmental support programs, nevertheless, this figure also implies to their satisfaction and also appreciation for these programs by business entities in both cities.
```{r}
# use
data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Options")+
  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()
```

According to figure 14, Peterborough restaurants are using more Canadian Emergency Wage Subsidy (CEWS)- a governmental program available for businesses to reimburse a considerable portion of their employees’ salaries – compared to Brantford restaurants. It is reasonable for Brantford restaurants to have utilized less of this grant because CEWS covers the wages partially and yet, the employer should pay the rest of the employee’s salary. This is also consistent with the results in figure 3 where they indicated to have had more layoffs.

@@

* Since the results of the presurvey suggest apparent similarities between the restaurants in Peterborough and those in Brantford, we assume the surveyed restaurants to have similar **qualities**. However, the attributes of the restaurants (size, employments, service type, etc) were not controlled in our analysis. In other words, we believe the response rate within the different restaurant subgroups to be the same. Variations in the actual response between restaurants in two cities are unknown and may impact the internal validity of the results.

* **The sample suffered from survivorship bias as we only surveyed restaurants that are still in operations. Restaurants that lost their businesses during the pandemic could not be captured with the current method. However, these may be the ones that are most severely impacted. Another aspect of the survivorship bias involves the use of the same sampling frame for the presurvey and the formal survey. Since there is a three-month time lag, some restaurants may be closed during that time.**

@@

```{r}
# readin the covid tracking data
covid_tracking <- readr::read_csv(here::here("inputs/data/simulated_covid_data.csv"))
```

### 2021-02-26 scripts/2178_chart_2.Rmd
Commit for data findings

pie(p_table_wage$Freq,labels = label_p,col=c( "#A6CEE3", "#1F78B4", "#B2DF8A" ),
    main = "Peterborough: Is your business receiving the Canada Emergency Wage Subsidy(CEWS)? ",cex=0.6,cex.main=1)

#Brantford
b_table_wage<- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q13_CEWS))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))

>>>>

pie(p_table_wage$Freq,labels = label_p,col=c( "#A6CEE3", "#1F78B4", "#B2DF8A" ),
    main = "Peterborough: Is your business receiving the Canada Emergency Wage Subsidy(CEWS)? ",cex=0.6,cex.main=1)
```

```{r}
# use
data.frame(table(simulated_dataset$q13_CEWS,simulated_dataset$q1_city))%>%
#  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
    geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Options")+
  ggtitle("Restaurants receiving the Canada Emergency Wage Subsidy(CEWS)")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()
```

```{r}
#Brantford
b_table_wage<- data.frame(table(simulated_dataset[simulated_dataset$q1_city=="Brantford",]$q13_CEWS))%>%
  mutate(pct=round(Freq/sum(Freq)*100,2))
